### 2025-01-30 MSE160 Lecture Notes/main.tex
jan 30

@@

\section{Geometric Descriptions of Crystals}

@@

\includepdf[pages=-, angle=90]{EquationSheet.pdf}
\end{document}

>>>>

    \item \textbf{Stacking} The FCC structure can be thought of as stacking close-packed planes. The stacking sequence is ABCABC... (where A, B, and C describe the orientation hexagonal close-packed planes).
\paragraph{Hexagonal Close-Packed (HCP)} The hexagonal close-packed structure is \textbf{crytal structure} by stacking close-packed hexagonal planes. It has the following properties:
    \item \textbf{Theortical Density} The theoretical density of HCP is derived from Equation (\ref{eq:theoretical-density}):
        \intertext{With $n = 6$ (12 corners $\times \frac{1}{6}$ atom each) and $V_c = a^3$:}
        \rho_\text{HCP} &= \frac{6M}{a^3 N_A} 
    \item \textbf{Atomic Packing Factor} The atomic packing factor of HCP is given by:
        \text{APF}_\text{HCP} = \frac{\text{Volume of atoms in unit cell}}{\text{Volume of unit cell} } = \frac{6 \times \frac{4}{3}\pi r^3}{a^3} = \frac{6 \times \frac{4}{3}\pi r^3}{a^3} = \textbf{0.74}
    \item \textbf{Stacking} The HCP structure can be thought of as stacking close-packed planes. The stacking sequence is ABAB...

@@

\paragraph{Body-Centered Cubic (BCC)} The body-centered cubic structure has an atom at the centre of the cube. It has the following properties:
    \item \textbf{Coordination Number} Number of nearest neighbor: 8
    \item \textbf{Atomic Packing Factor} The atomic packing factor of BCC is given by:
        \text{APF}_\text{BCC} = \frac{\text{Volume of atoms in unit cell}}{\text{Volume of unit cell} } = \frac{2 \times \frac{4}{3}\pi r^3}{a^3} = \frac{2 \times \frac{4}{3}\pi r^3}{(4r/\sqrt{3})^3} = \textbf{0.68}
    \item \textbf{Close Packed Directions} As cube diagonals.
    \item \textbf{Theortical Density} The theoretical density of BCC is derived from Equation (\ref{eq:theoretical-density}):
        \intertext{With $n = 2$ (8 corners $\times \frac{1}{8}$ atom each + 1 center atom) and $V_c = a^3$:}
        \rho_\text{BCC} &= \frac{2M}{a^3 N_A} 
    \item \textbf{Stacking} The BCC structure can be thought of as stacking close-packed planes. The stacking sequence is ABAB...
\section{Geometric Properties of Crystals}

@@

\subsection{X-Ray Diffraction} The diffraction pattern is used to determine the crystal structure. By measuring the n$^\text{th}$ order peak angle $\theta_c$ and the wavelength of the X-ray, we can determine the distance between planes:
    2d\sin \theta &= n\lambda \nonumber \\
    d &= \frac{n\lambda}{2\sin \theta_c}
    \intertext{Thus, we could determine the lattice parameter $a$ by the following equation:}
    a &= \frac{n\lambda}{2\sin \theta_c} \sqrt{h^2 + k^2 + l^2}

\includepdf[pages=-, angle=90]{EquationSheet.pdf}
\end{document}
